### 2019-02-16 sections/intuition.tex
intuition: tasks are reusable

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, with which users can
interact, and combinators to express ways in which people can work together on
these tasks. Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

Tasks are extremely flexible. They are modular; \fixme{why exactly?}. Tasks are
composable, using the aforementioned combinators. And tasks are higher order;
they can be abstracted over zero or more arguments, and those arguments could
be tasks themselves.

@@

A simple higher-order task which performs a task twice can be specified as
follows.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x : $\tau$. t
\end{TASK}
By using the step combinator $\Next$ we specify that the given task \TS{t}
should be performed a second time. The result \TS{x} from the first run is
ignored.

@@

\fixme{conclude something about why this is convenient}

>>>>

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, with which users can
interact, and combinators to express ways in which people can work together.
Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

Tasks are modular in the following ways.
First, larger tasks are composed from smaller ones.
Second, tasks are first-class, they can be arguments and results of functions.
Third, tasks can be values of other tasks.
These aspects make it possible for programmers to model custom collaboration patterns.

@@

A higher-order function which executes a given task twice.
The task value of the first execution is ignored.

\fixme{Is that our official syntax?}
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x : $\tau$
\end{TASK}
\qed

@@
